An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-13 ex3/paper/paper.tex
Undid ars motivation change

Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

>>>>

Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
